GAM

### 2023-07-30 Analysis/ME_Slopes.qmd
updating scripts with new data file

```{r setup}
pacman::p_load(tidyverse,tidybayes, brms, broom, broom.mixed, lme4,emmeans,here,knitr,kableExtra,gt,ggh4x)
e1 <- readRDS(here("data/e1_07_04_23.rds"))
source(here("Functions/Display_Functions.R"))

>>>>

```{r setup}
pacman::p_load(tidyverse,tidybayes, brms, broom, broom.mixed, lme4,emmeans,here,knitr,kableExtra,gt,ggh4x)
e1 <- readRDS(here("data/e1_07-27-23.rds"))
source(here("Functions/Display_Functions.R"))

### 2023-07-30 Analysis/data_dictionary.qmd
updating scripts with new data file

```{r}
pacman::p_load(tidyverse, lme4, emmeans, here, knitr, kableExtra,gt)
options(dplyr.summarise.inform = FALSE)
d <- readRDS(here("data/dPrune-05-21-23.rds")) %>% ungroup()
d$stage <- factor(d$stage, ordered = TRUE, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "22", "23"))
d$tOrder <- factor(d$tOrder, levels = c("testFirst", "trainFirst"), labels = c("Test First", "Train First"))
d$bandOrder <- factor(d$catOrder, levels = c("orig", "rev"), labels = c("Original", "Reverse"))
d$fb <- factor(d$fb, levels = c("continuous", "ordinal"), labels = c("Continuous", "Ordinal"))
d <- d %>%
    mutate(id = as.factor(d$id), fullCond = as.factor(fullCond)) %>%
    select(-catOrder, -mode) %>%
    relocate(bandOrder, .after = fb)

@@

>>>>

```{r}
pacman::p_load(tidyverse, lme4, emmeans, here, knitr, kableExtra,gt)
options(dplyr.summarise.inform = FALSE)
d <- readRDS(here("data/dPrune-07-27-23.rds")) %>% ungroup()
d$stage <- factor(d$stage, ordered = TRUE, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "22", "23"))
d$tOrder <- factor(d$tOrder, levels = c("testFirst", "trainFirst"), labels = c("Test First", "Train First"))
d$bandOrder <- factor(d$bandOrder, levels = c("orig", "rev"), labels = c("Original", "Reverse"))
d$fb <- factor(d$fb, levels = c("continuous", "ordinal"), labels = c("Continuous", "Ordinal"))
d <- d %>%
    mutate(id = as.factor(d$id), fullCond = as.factor(fullCond)) %>%
    relocate(bandOrder, .after = fb)

@@

----------

id - unique subject identifier 
condit - primary training manipulation, Constant vs. Varied. 
tOrder - whether testing phase starts with extrapolation testing
expMode2

### 2023-07-30 Analysis/gam_discrim.qmd
updating scripts with new data file

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,mgcv,data.table)
e1 <- readRDS(here("data/e1_07_04_23.rds"))
source(here("Functions/Display_Functions.R"))

>>>>

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,mgcv,data.table)
e1 <- readRDS(here("data/e1_07_27_23.rds"))
source(here("Functions/Display_Functions.R"))
